\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{First Last}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{abdullaharif.tech}
% vs how you want it to show up. If it's you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://abdullaharif.tech}
\newcommand{\yourEmail}{someEmail@edu.com}
\newcommand{\yourPhone}{1-234-567-890}
\newcommand{\githubUserName}{aarif123456}
\newcommand{\linkedInUserName}{abdullaharif98}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{https://\yourWebsite}{\underline{\yourWebsite}} $|$ 
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{BSc. Honours Computer Science With Software Engineering Specialization}{University of Windsor}{Windsor, ON}{Jun 2021}

\teacherAssistant{World Wide Web Information Systems Development}
% \courseWork{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Amazon}{Software Development Engineer Intern}{Toronto, ON}{May 2020 – Aug 2020}
\begin{bullets}
    \item Designed and implemented a dashboard using \textbf{React} and \textbf{TypeScript} to visualize data stored in \textbf{DynamoDB}, decreasing time to understand delivery driver work sessions by over 10 times.
    %  \item Here is another bullet that I might choose to uncomment for some jobs
    \item Ensured only authorized employees have access to the application by creating an \textbf{AWS Lambda@Edge} function to intercept and sign valid requests.
    \item Devised and deployed the infrastructure in TypeScript through \textbf{AWS CDK}, then created efficient algorithms to process data from a custom \textbf{REST API}, so it could scale to handle millions of deliveries.
    \item Setup a CI/CD pipeline and exceeded requirements in each stage, which lead to the application being pushed to production.
\end{bullets}
\sectionsep

\resumeHeading{University of Windsor}{Research Assistant (RA)}{Windsor, ON}{Feb 2020 - May 2020}
\begin{bullets}
    \item Developed a Personal Health Record (PHR) system in \textbf{\href{https://spring.io/}{Spring}} based on the theoretical model outlined in \underlinedLink{https://research.library.mun.ca/11920}{Mitu Kumar's thesis}.
    \item Applied the \href{https://link.springer.com/chapter/10.1007/978-3-642-10838-9\_23}{mCP-ABE} encryption scheme using the \href{http://gas.dia.unisa.it/projects/jpbc/}{JPBC} library, so patients have fine-grained access control over their health records with the ability to instantly revoke access.
\end{bullets}
\sectionsep

\resumeHeading{JoaTu}{Software Engineer Intern}{Montreal, QC}{Dec 2018 – May 2019}
\begin{bullets}
    \item Rewrote legacy \textbf{Django code} in \textbf{Ruby in Rails} and refactored it to make the system more extensible.
    \item Created \textbf{UML} diagrams and documented where features were implemented, to make the codebase more maintainable.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeading{Automated Spear-Phisher}{https://github.com/Aarif123456/Fb-Twitter-gui}{Python, PySpark, Selenium, Apache, NLP, Big Data}
A security research tool to send targeted spam messages on either Facebook or Twitter. The program analyzes the feed of its target to increase the effectiveness of the messages.\\
\sectionsep
  
\projectHeading{Image Repository}{https://github.com/Aarif123456/image\_repository}{Java, PHP, React, TypeScript, Maven, GCP, MySQL}
A full-stack image repository, where users can store their files. Created a GCP cloud function to implement \href{https://www.cs.utexas.edu/~bwaters/publications/papers/cp-abe.pdf}{CP-ABE} encryption and used it to ensure files are secure at rest.\\
\sectionsep

\projectHeading{Biometric Dynamic Keystroke Spoofer}{https://github.com/Aarif123456/KeystrokeDynamicsSpoofer}{Python, Object-Oriented Design, CyberSecurity}
A program that authenticates users based on their typing patterns. And a spoofer that uses the genetic algorithm to mimic the user's typing pattern.
\sectionsep

\projectHeading{Distributed Key-Value store}{https://github.com/Aarif123456/Distributed-DB}{Java, Distributed System, Computer Networks, Concurrency}
A distributed key-value store which automatically replicates data in the background while the user manages their data. Implemented a custom P2P protocol to maximize fault tolerance and scalability.\\
\sectionsep

\projectHeading{War of Weebles}{https://github.com/Aarif123456/GoalOrientedBehaviour}{C\#, Unity, Concurrency, Artificial Intelligence}
A capture-the-flag-styled shooting game composed of AI-controlled players. The agents change their goals based on various factors, such as their health, current weapon, their personality and what they see.\\
\sectionsep

% Example using bullets and dates 
% \projectHeadingWithDate{Hogwart\textquotesingle{}s Library Management System}{https://github.com/Aarif123456/hogwartslibrary}{PHP, JavaScript, HTML, CSS, MySQL}{Aug 2019}
% \begin{bullets}
    % \item A full-stack library management system, where users can manage books and holds on their accounts. Users can search the library\textquotesingle{}s catalogue, which has every book mentioned in the Harry Potter series. The system distinguishes between 4 users. For examples, librarians who can also check or return books on behalf of users.\\
% \end{bullets}
% \sectionsep
  

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket, SQL}
    \\
    \singleItem{Web Development:}{React, JavaScript, TypeScript, HTML/CSS}
    \\
    \singleItem{Technology:}{Git, AWS, GCP, Azure, Docker, Unity, Apache, \LaTeX, MongoDB, DynamoDB, Neo4j}
\end{skillList}

% A more concise alternate 
% \begin{skillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket}%
%     {Databases:}{SQL, MongoDB, Neo4j, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{skillList}
\end{document}
